---
title: "Complete CAFI Survey Analysis Compendium"
subtitle: "All Analyses & Results — Coral-Associated Fauna of Mo'orea, French Polynesia"
author: "CAFI Research Team"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: hide
    fig_width: 12
    fig_height: 8
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  out.width = "100%"
)

library(tidyverse)
library(kableExtra)

# Set base path
base_path <- here::here()
if (!dir.exists(base_path)) base_path <- "/Users/adrianstiermbp2023/CAFI-Survey-2026"

fig_path <- file.path(base_path, "output/figures")
```

# Executive Summary {-}

This document is a **100% comprehensive compendium** of all analyses conducted on the CAFI (Coral-Associated Fauna Inventory) survey data. It consolidates results from **47+ R scripts** and **153 figures** across the repository.

## Master Hypothesis Summary {-}

| Hypothesis | Question | Result | Key Statistic |
|:-----------|:---------|:-------|:--------------|
| **H1** | Community composition differs among sites? | **SUPPORTED** | R² = 0.18, p < 0.001 |
| **H2** | CAFI abundance scales sublinearly with coral size? | **SUPPORTED** | β = 0.49 [0.40, 0.57] |
| **H3** | Neighborhood effects matter beyond coral size? | **NOT SUPPORTED** | <1% ΔR² |
| **H4** | CAFI diversity predicts coral condition? | **NOT SUPPORTED** | Sampling artifact |
| **H5** | Networks show non-random structure? | **SUPPORTED** | Transitivity 3.8× null |

## Complete Analysis Categories {-}

1. Data Loading & Quality Control
2. Community Composition (PERMANOVA, NMDS)
3. Diversity Analysis (α, β, γ)
4. Power-Law Scaling (H2)
5. Neighborhood Effects (H3)
6. Coral Characteristics & Physiology
7. Position Correction (Stump Length)
8. CAFI-Coral Condition Relationships
9. Diversity-Condition Analysis (H4)
10. Network Analysis (H5)
11. Spatial Autocorrelation (Moran's I, LISA)
12. Size-Biomass Scaling
13. Machine Learning (RF, XGBoost, SDMs)
14. Comprehensive Predictor Analysis
15. Trapezid Guardian Crab Analysis
16. Morphotype/Habitat Analysis
17. db-RDA Composition Analysis
18. NMDS Outlier Investigation
19. Variance Partitioning

---

# Data Overview & Quality Control

## Study System

```{r study-system, out.width="90%"}
study_fig <- file.path(fig_path, "manuscript/Figure1_study_system.png")
if (file.exists(study_fig)) {
  knitr::include_graphics(study_fig)
} else {
  cat("Figure not available")
}
```

## Dataset Summary

```{r load-summary-data}
# Load data for summary statistics
cafi_data <- read.csv(file.path(base_path, "data/survey_cafi_data_w_taxonomy_summer2019_v5.csv"))
coral_data <- read.csv(file.path(base_path, "data/survey_coral_characteristics_merged_v2.csv"))

summary_stats <- tibble(
  Metric = c("Total coral colonies sampled", "Total CAFI individuals",
             "Unique CAFI OTUs", "Sites surveyed",
             "Depth range (m)", "Coral volume range (cm³)"),
  Value = c(nrow(coral_data),
            nrow(cafi_data),
            n_distinct(paste(cafi_data$genus, cafi_data$species)),
            "3 (HAU, MAT, MRB)",
            "1-12",
            "10-15,000+")
)

kable(summary_stats, caption = "Dataset Overview") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

::: {.alert .alert-info}
**Important: Two Survey Types**

The study employed two complementary sampling designs:

- **Neighborhood surveys (n = 63)**: Corals POC01-POC21 at each site received full 5-meter radius surveys documenting all neighboring *Pocillopora* colonies
- **Size surveys (n = 51)**: Corals POC22+ at each site were surveyed for size and CAFI only—*no neighborhood data collected*

**Neighborhood analyses use ONLY the 63 corals with actual neighborhood surveys.** Community composition and scaling analyses use all 114 corals.
:::

---

# Community Composition Analysis {.tabset}

## Species Rank-Abundance

```{r rank-abundance-fig, out.width="90%"}
fig <- file.path(fig_path, "community_composition/species_rank_abundance.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Taxonomic Composition

```{r taxonomic-pie, out.width="80%"}
fig <- file.path(fig_path, "community_composition/taxonomic_composition_pie.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Top Species Heatmap

```{r species-heatmap, out.width="100%"}
fig <- file.path(fig_path, "community_composition/top_species_heatmap.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Community Stacked Bar

```{r community-stacked, out.width="100%"}
fig <- file.path(fig_path, "community_composition/community_composition_stacked.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Species Accumulation Curves

```{r species-accumulation, out.width="90%"}
fig <- file.path(fig_path, "community_composition/species_accumulation_curves.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Site Diversity Metrics

```{r site-diversity, out.width="90%"}
fig <- file.path(fig_path, "community_composition/site_diversity_metrics.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Size Distribution by Type

```{r size-by-type, out.width="90%"}
fig <- file.path(fig_path, "community_composition/size_distribution_by_type.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Diversity Analysis {.tabset}

## NMDS Ordination (Cleaned)

```{r nmds-cleaned, out.width="100%"}
fig <- file.path(fig_path, "diversity/nmds_ordination_cleaned.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## NMDS Excluded Corals Comparison

```{r nmds-excluded, out.width="100%"}
fig <- file.path(fig_path, "diversity/nmds_excluded_comparison.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## NMDS Outlier Investigation {.tabset}

### Outliers Highlighted

```{r nmds-outliers-1, out.width="100%"}
fig <- file.path(fig_path, "nmds_outliers/01_nmds_outliers_highlighted.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

### By Abundance

```{r nmds-outliers-2, out.width="100%"}
fig <- file.path(fig_path, "nmds_outliers/02_nmds_by_abundance.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

### By Richness

```{r nmds-outliers-3, out.width="100%"}
fig <- file.path(fig_path, "nmds_outliers/03_nmds_by_richness.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

### Outlier Comparison

```{r nmds-outliers-4, out.width="100%"}
fig <- file.path(fig_path, "nmds_outliers/04_outlier_comparison_boxplots.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

### Composition Comparison

```{r nmds-outliers-5, out.width="100%"}
fig <- file.path(fig_path, "nmds_outliers/05_composition_comparison.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Hypothesis 2: Power-Law Scaling {.tabset}

**Question:** Does CAFI abundance scale sublinearly with coral volume?

**Result:** ✓ **SUPPORTED** — β = 0.49 [95% CI: 0.40–0.57], significantly less than 1.0

## Scaling Figure (Manuscript)

```{r scaling-manuscript, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure3_scaling.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Coral Size Effects

```{r size-effects, out.width="100%"}
fig <- file.path(fig_path, "comprehensive_predictors/coral_size_effects.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Size-Abundance Models

```{r size-abundance-models, out.width="100%"}
fig <- file.path(fig_path, "size_neighbor_effects/size_abundance_models.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Hypothesis 3: Neighborhood Effects {.tabset}

**Question:** Do local coral neighborhood characteristics affect CAFI beyond focal coral size?

**Result:** ✗ **NOT SUPPORTED** — <1% additional variance explained

::: {.alert .alert-warning}
**Sample Note:** Neighborhood analyses use only the **63 corals** with 5m radius neighborhood surveys (POC01-POC21 at each site). The 51 "size" corals were not surveyed for neighbors and have `NA` for neighborhood metrics.
:::

## Neighbor Effects Overview

```{r neighbor-effects, out.width="100%"}
fig <- file.path(fig_path, "comprehensive_predictors/neighbor_effects.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Neighborhood Effects (Manuscript)

```{r neighborhood-manuscript, out.width="100%"}
fig <- file.path(fig_path, "neighborhood_effects/Figure6_comprehensive_neighborhood.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Depth Effects by Site

```{r depth-effects, out.width="100%"}
fig <- file.path(fig_path, "comprehensive_predictors/depth_effects_by_site.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Coral Characteristics & Physiology {.tabset}

## Sampling Position Bias

The stump length (position along branch) confounds physiology measurements. All physiological metrics are corrected for this bias.

```{r position-bias-1, out.width="100%"}
fig <- file.path(fig_path, "coral_characteristics/01_sampling_position_bias.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Position by Size Quintile

```{r position-quintile, out.width="100%"}
fig <- file.path(fig_path, "coral_characteristics/02_position_by_size_quintile.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Correlation Heatmap (Corrected)

```{r corr-heatmap, out.width="90%"}
fig <- file.path(fig_path, "coral_characteristics/03_correlation_heatmap_corrected.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## PCA Scree Plot

```{r pca-scree, out.width="80%"}
fig <- file.path(fig_path, "coral_characteristics/04_pca_scree_plot.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## PCA Biplot

```{r pca-biplot, out.width="100%"}
fig <- file.path(fig_path, "coral_characteristics/05_pca_biplot.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Size Effects on Corrected Traits

```{r size-corrected-traits, out.width="100%"}
fig <- file.path(fig_path, "coral_characteristics/06_size_effects_corrected_traits.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Condition Score by Site

```{r condition-site, out.width="90%"}
fig <- file.path(fig_path, "coral_characteristics/07_condition_score_by_site.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Condition Score vs Size

```{r condition-size, out.width="90%"}
fig <- file.path(fig_path, "coral_characteristics/08_condition_score_vs_size.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Condition Trait Profiles

```{r condition-profiles, out.width="100%"}
fig <- file.path(fig_path, "coral_characteristics/09_condition_trait_profiles.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# CAFI-Coral Relationships {.tabset}

## CAFI Overall Abundance

```{r cafi-abundance, out.width="90%"}
fig <- file.path(fig_path, "coral_cafi_relationships/cafi_overall_abundance.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## CAFI by Location

```{r cafi-location, out.width="100%"}
fig <- file.path(fig_path, "coral_cafi_relationships/cafi_by_location.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## CAFI by Branch Width

```{r cafi-branch, out.width="90%"}
fig <- file.path(fig_path, "coral_cafi_relationships/cafi_by_branch_width.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Taxonomic Composition by Site

```{r taxa-by-site, out.width="100%"}
fig <- file.path(fig_path, "coral_cafi_relationships/taxonomic_composition_by_site.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## CAFI vs Coral Condition

```{r cafi-vs-condition, out.width="100%"}
fig <- file.path(fig_path, "coral_cafi_relationships/cafi_vs_coral_condition.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## CAFI vs Condition by Site

```{r cafi-condition-site, out.width="100%"}
fig <- file.path(fig_path, "coral_cafi_relationships/cafi_vs_condition_by_site.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Richness vs Coral Condition

```{r richness-condition, out.width="100%"}
fig <- file.path(fig_path, "coral_cafi_relationships/richness_vs_coral_condition.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## CAFI vs Physiology Panel

```{r cafi-physio-panel, out.width="100%"}
fig <- file.path(fig_path, "coral_cafi_relationships/cafi_vs_physiology_panel.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## CAFI vs Corrected Traits Panel

```{r cafi-corrected-panel, out.width="100%"}
fig <- file.path(fig_path, "coral_cafi_relationships/cafi_vs_corrected_traits_panel.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Richness vs Corrected Traits

```{r richness-corrected, out.width="100%"}
fig <- file.path(fig_path, "coral_cafi_relationships/richness_vs_corrected_traits_panel.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## CAFI Trait Coefficients

```{r trait-coefficients, out.width="90%"}
fig <- file.path(fig_path, "coral_cafi_relationships/cafi_trait_coefficients.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Model Coefficients

```{r model-coefficients, out.width="90%"}
fig <- file.path(fig_path, "coral_cafi_relationships/model_coefficients.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Hypothesis 4: Diversity-Condition {.tabset}

**Question:** Does CAFI diversity predict coral physiological condition?

**Result:** ✗ **NOT SUPPORTED** — Apparent relationship is a sampling artifact

## CAFI-Condition Manuscript Figure

```{r cafi-condition-manuscript, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure4_cafi_condition.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## CAFI Predicts Condition Analysis

```{r cafi-predicts-condition, out.width="100%"}
figs <- list.files(file.path(fig_path, "cafi_predicts_condition"), pattern = "\\.png$", full.names = TRUE)
if (length(figs) > 0) {
  for (f in head(figs, 4)) {
    cat("\n\n")
    print(knitr::include_graphics(f))
  }
}
```

---

# Hypothesis 5: Network Structure {.tabset}

**Question:** Do CAFI co-occurrence networks exhibit non-random modular structure?

**Result:** ✓ **SUPPORTED** — Transitivity 3.8× null, Modularity Q = 0.52

## Network Manuscript Figure

```{r network-manuscript, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure5_network.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Co-occurrence Network

```{r cooccurrence-network, out.width="100%"}
fig <- file.path(fig_path, "network_analysis/01_cafi_cooccurrence_network.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Network Modules

```{r network-modules, out.width="100%"}
fig <- file.path(fig_path, "network_analysis/02_cafi_network_modules.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Keystone Species Ranking

```{r keystone-ranking, out.width="90%"}
fig <- file.path(fig_path, "network_analysis/03_keystone_species_ranking.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Condition vs Network Degree

```{r condition-network-degree, out.width="100%"}
fig <- file.path(fig_path, "network_analysis/04_condition_vs_cafi_network_degree.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Condition vs Keystone Presence

```{r condition-keystone, out.width="100%"}
fig <- file.path(fig_path, "network_analysis/05_condition_vs_keystone_presence.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Coral Size vs Network Degree

```{r size-network-degree, out.width="100%"}
fig <- file.path(fig_path, "network_analysis/10_coral_size_vs_network_degree.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Module Taxonomic Composition

```{r module-taxa, out.width="100%"}
fig <- file.path(fig_path, "network_analysis/08_module_taxonomic_composition.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Spatial Analysis {.tabset}

## Survey Locations Map

```{r survey-map, out.width="100%"}
fig <- file.path(fig_path, "spatial_patterns/survey_locations_map.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Depth Distribution

```{r depth-dist, out.width="90%"}
fig <- file.path(fig_path, "spatial_patterns/depth_distribution.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Richness vs Depth

```{r richness-depth, out.width="90%"}
fig <- file.path(fig_path, "spatial_patterns/richness_vs_depth.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Spatial Autocorrelation {.tabset}

### Moran's I Scatterplot

```{r moran-scatter, out.width="90%"}
fig <- file.path(fig_path, "spatial_analysis/moran_scatterplot_abundance.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

### LISA Cluster Map

```{r lisa-map, out.width="100%"}
fig <- file.path(fig_path, "spatial_analysis/lisa_cluster_map.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

### Mantel Test

```{r mantel-test, out.width="90%"}
fig <- file.path(fig_path, "spatial_analysis/mantel_test_plot.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

### Spatial Interpolation

```{r spatial-interp, out.width="100%"}
fig <- file.path(fig_path, "spatial_analysis/spatial_interpolation_abundance.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Size-Biomass Scaling {.tabset}

## Community Size Spectrum

```{r size-spectrum, out.width="100%"}
fig <- file.path(fig_path, "size_biomass_scaling/community_size_spectrum.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Taxonomic Size Distributions

```{r taxa-size-dist, out.width="100%"}
fig <- file.path(fig_path, "size_biomass_scaling/taxonomic_size_distributions.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Biomass-Abundance Scaling

```{r biomass-abundance, out.width="100%"}
fig <- file.path(fig_path, "size_biomass_scaling/biomass_abundance_scaling.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Machine Learning {.tabset}

## Random Forest Variable Importance

```{r rf-importance, out.width="90%"}
fig <- file.path(fig_path, "machine_learning/rf_variable_importance.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## RF Predictions vs Actual

```{r rf-predictions, out.width="90%"}
fig <- file.path(fig_path, "machine_learning/rf_predictions_vs_actual.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## XGBoost Feature Importance

```{r xgb-importance, out.width="90%"}
fig <- file.path(fig_path, "machine_learning/xgboost_feature_importance.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Model Comparison

```{r model-comparison, out.width="90%"}
fig <- file.path(fig_path, "machine_learning/model_comparison_boxplot.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Advanced Statistical Models {.tabset}

## GLMM Coefficients

```{r glmm-coefs, out.width="90%"}
fig <- file.path(fig_path, "advanced_models/glmm_coefficients_abundance.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Model Diagnostics

```{r model-diagnostics, out.width="100%"}
fig <- file.path(fig_path, "advanced_models/model_diagnostics_abundance.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Variance Partitioning

```{r variance-part, out.width="90%"}
fig <- file.path(fig_path, "advanced_models/variance_partitioning.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Richness Model Predictions

```{r richness-predictions, out.width="100%"}
fig <- file.path(fig_path, "advanced_models/richness_model_predictions.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# db-RDA Composition Analysis {.tabset}

## RDA Composition Figure

```{r rda-composition, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure8_rda_composition.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Composition Figures

```{r composition-figs, out.width="100%"}
figs <- list.files(file.path(fig_path, "composition"), pattern = "\\.png$", full.names = TRUE)
if (length(figs) > 0) {
  for (f in figs) {
    cat("\n\n")
    print(knitr::include_graphics(f))
  }
}
```

---

# Trapezid Guardian Crab Analysis {.tabset}

Trapezids (Family Trapeziidae) are obligate coral symbionts that defend Pocillopora from predators.

## Trapezids by Site

```{r trapezids-site, out.width="90%"}
fig <- file.path(fig_path, "trapezid_analysis/trapezids_by_site.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Trapezids vs Tissue Biomass

```{r trapezids-biomass, out.width="90%"}
fig <- file.path(fig_path, "trapezid_analysis/trapezids_vs_tissue_biomass.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Condition vs Landscape {.tabset}

## Condition vs Size

```{r cond-size, out.width="90%"}
fig <- file.path(fig_path, "condition_vs_landscape/condition_vs_size.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Condition by Site

```{r cond-site, out.width="90%"}
fig <- file.path(fig_path, "condition_vs_landscape/condition_by_site.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Condition vs Neighborhood Panel

```{r cond-neighbor, out.width="100%"}
fig <- file.path(fig_path, "condition_vs_landscape/condition_vs_neighborhood_panel.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Correlation Matrix

```{r cond-corr, out.width="100%"}
fig <- file.path(fig_path, "condition_vs_landscape/condition_landscape_correlation_matrix.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Individual Physiology vs Size

```{r physio-size, out.width="100%"}
fig <- file.path(fig_path, "condition_vs_landscape/individual_physio_vs_size.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Comprehensive Summary {.tabset}

## Results Dashboard

```{r results-dashboard, out.width="100%"}
fig <- file.path(fig_path, "comprehensive_summary/results_dashboard.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Predictor Overview

```{r predictor-overview, out.width="100%"}
fig <- file.path(fig_path, "comprehensive_summary/predictor_overview.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Model Comparison Summary

```{r model-comp-summary, out.width="100%"}
fig <- file.path(fig_path, "comprehensive_summary/model_comparison.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Comprehensive Summary Figure

```{r comprehensive-summary, out.width="100%"}
fig <- file.path(fig_path, "comprehensive_summary/comprehensive_summary.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Predictor Correlation Matrix

```{r predictor-corr, out.width="100%"}
fig <- file.path(fig_path, "comprehensive_predictors/predictor_correlation_matrix.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# All Manuscript Figures {.tabset}

## Figure 1: Study System

```{r ms-fig1, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure1_study_system.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Figure 2: Community Composition

```{r ms-fig2, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure2_community_composition.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Figure 3: Size Scaling

```{r ms-fig3, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure3_scaling.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Figure 4: CAFI-Condition

```{r ms-fig4, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure4_cafi_condition.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Figure 5: Network Analysis

```{r ms-fig5, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure5_network.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

## Figure 8: RDA Composition

```{r ms-fig8, out.width="100%"}
fig <- file.path(fig_path, "manuscript/Figure8_rda_composition.png")
if (file.exists(fig)) knitr::include_graphics(fig)
```

---

# Summary of Key Findings

## What Matters for CAFI Assembly

1. **Coral Size** — Dominant predictor (~56% of abundance variance)
   - Sublinear scaling (β = 0.49): larger corals have proportionally fewer CAFI per unit volume
   - Consistent with propagule redirection hypothesis

2. **Reef Site** — ~18% of compositional variance
   - Sites harbor distinct CAFI assemblages
   - Environmental filtering at landscape scale

3. **Network Structure** — Non-random co-occurrence
   - Transitivity 3.8× null expectation
   - Modularity Q = 0.52 (strong modular structure)
   - Predictable species associations

## What Doesn't Matter (at scales measured)

1. **Neighborhood Effects** — <1% additional variance beyond size
   - 5m measurement scale may be too small
   - Propagule dynamics may operate at 10s-100s of meters

2. **Coral Condition** — No effect on CAFI
   - Diversity-condition relationship is sampling artifact
   - Position correction eliminates apparent relationships

3. **Raw Diversity Metrics** — Confounded by abundance
   - Must use rarefied or residualized richness

## Practical Implications

- **Restoration**: Size distribution matters more than coral spacing
- **Mixed-size strategy**: Small corals maximize density; large corals support distinct communities
- **Site selection**: Different reef environments support different CAFI assemblages

---

# Statistical Methods Summary

| Category | Methods | R Packages |
|:---------|:--------|:-----------|
| Multivariate | PERMANOVA, NMDS, PERMDISP, db-RDA | vegan |
| Scaling | Log-log regression, Mixed models | lme4, lmerTest |
| Non-linear | GAMs with smooth terms | mgcv |
| Count models | GLMM (negative binomial) | glmmTMB |
| Machine Learning | Random Forest, XGBoost | randomForest, xgboost |
| Networks | Co-occurrence, null models | igraph |
| Spatial | Moran's I, LISA, Mantel | spdep, ape |
| Variance partitioning | varpart | vegan |

---

# Session Information

```{r session-info}
sessionInfo()
```

---

*Document generated: `r Sys.time()`*

*Complete CAFI Survey Analysis Compendium v3.0*

*Consolidates 47+ R scripts and 153 figures from the analysis pipeline*
