---
title: "Supplementary Materials"
subtitle: "Landscape characteristics structure coral-associated fauna communities and their functional effects on coral condition"
author: "Stier et al."
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    self_contained: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  out.width = "100%",
  dpi = 150
)

library(here)
library(knitr)
library(tidyverse)
library(kableExtra)
```

<style>
/* =============================================
   SUPPLEMENTARY MATERIALS - OPTIMIZED CSS
   ============================================= */

/* Base Typography - WIDER CONTENT */
body {
  font-family: 'Georgia', 'Times New Roman', serif;
  font-size: 11.5pt;
  line-height: 1.65;
  color: #2d3436;
  max-width: 1600px;
  margin: 0 auto;
  padding: 25px 40px;
  background: #fff;
}

/* Main content container - leave space for TOC */
.main-container {
  max-width: 1300px;
  margin-left: 220px;
  padding: 0 30px;
}

/* TOC - Fixed left sidebar */
.tocify {
  width: 190px !important;
  position: fixed !important;
  left: 20px !important;
  top: 80px !important;
  max-height: calc(100vh - 100px);
  overflow-y: auto !important;
  font-size: 9pt !important;
  border: 1px solid #e0e0e0 !important;
  border-radius: 6px !important;
  background: #fff !important;
  box-shadow: 0 2px 8px rgba(0,0,0,0.06);
  z-index: 1000;
}

.tocify-item { padding: 7px 10px !important; }
.tocify .active { background: #0984e3 !important; color: white !important; border-radius: 0 4px 4px 0 !important; }
.tocify-subheader { font-size: 8.5pt !important; }

@media (max-width: 1000px) {
  body { padding: 20px 25px; max-width: 100%; }
  .main-container { margin-left: 0; max-width: 100%; }
  .tocify { position: relative !important; left: 0 !important; top: 0 !important; width: 100% !important; max-height: none; margin-bottom: 25px; }
}

h1.title { font-size: 20pt; font-weight: 700; text-align: center; margin-bottom: 8px; line-height: 1.3; color: #1a252f; }
.subtitle { font-size: 11pt; text-align: center; font-style: italic; color: #555; margin-bottom: 10px; }
.author { text-align: center; font-size: 11pt; color: #666; margin-bottom: 25px; }

h1 { font-size: 15pt; font-weight: 700; color: #1a252f; border-bottom: 2px solid #0984e3; padding-bottom: 6px; margin-top: 35px; margin-bottom: 15px; text-transform: uppercase; letter-spacing: 0.5px; }
h2 { font-size: 13pt; font-weight: 600; color: #2d3436; margin-top: 25px; margin-bottom: 12px; border-left: 4px solid #0984e3; padding-left: 12px; }
h3 { font-size: 11.5pt; font-weight: 600; font-style: italic; color: #555; margin-top: 18px; margin-bottom: 8px; }

p { text-align: justify; margin-bottom: 12px; hyphens: auto; }

table { width: 100%; border-collapse: collapse; margin: 18px 0; font-size: 10pt; background: #fff; box-shadow: 0 1px 4px rgba(0,0,0,0.06); border-radius: 4px; overflow: hidden; }
thead { background: linear-gradient(135deg, #2d3436 0%, #3d4a4f 100%); }
th { background: transparent; color: white; padding: 12px 10px; text-align: left; font-weight: 600; text-transform: uppercase; font-size: 9pt; letter-spacing: 0.3px; }
td { padding: 10px; border-bottom: 1px solid #eee; vertical-align: top; }
tbody tr:hover { background: #f8f9fa; }
tbody tr:last-child td { border-bottom: none; }

.figure { margin: 25px 0; padding: 15px; background: #fafbfc; border: 1px solid #e0e0e0; border-radius: 8px; }
.figure img { max-width: 100%; height: auto; display: block; margin: 0 auto; border-radius: 4px; }
figcaption, .caption { font-size: 10pt; color: #555; margin-top: 12px; line-height: 1.55; text-align: left; padding-top: 10px; border-top: 1px solid #eee; }

.toc-box { background: linear-gradient(135deg, #f8f9fa 0%, #e9ecef 100%); border: 1px solid #dee2e6; border-left: 4px solid #0984e3; border-radius: 0 8px 8px 0; padding: 18px 22px; margin: 25px 0; }
.toc-box strong { color: #0984e3; font-size: 11pt; }

.methods-box { background: linear-gradient(135deg, #e3f2fd 0%, #bbdefb 100%); border-left: 4px solid #1976d2; padding: 18px 22px; margin: 20px 0; border-radius: 0 8px 8px 0; }
.methods-box strong { color: #1565c0; }

.cross-ref { background: #fff3cd; border-left: 4px solid #ffc107; padding: 12px 18px; margin: 15px 0; border-radius: 0 6px 6px 0; font-size: 10pt; }
.cross-ref strong { color: #856404; }

.hypothesis-box { background: linear-gradient(135deg, #e8f5e9 0%, #c8e6c9 100%); border-left: 4px solid #4caf50; padding: 15px 18px; margin: 15px 0; border-radius: 0 6px 6px 0; }
.hypothesis-box strong { color: #2e7d32; }

.reproducibility { background: #d4edda; border-left: 4px solid #28a745; padding: 12px 18px; margin: 15px 0; border-radius: 0 6px 6px 0; font-size: 9.5pt; }
.reproducibility code { background: #c3e6cb; padding: 2px 6px; border-radius: 3px; font-size: 9pt; }

.equation { background: #f5f5f5; padding: 15px 25px; margin: 15px 0; border-radius: 6px; text-align: center; border: 1px solid #e0e0e0; }

pre, code { font-family: 'SF Mono', 'Consolas', 'Monaco', monospace; font-size: 9.5pt; }
pre { background: #2d3436; color: #dfe6e9; padding: 15px 18px; border-radius: 6px; overflow-x: auto; margin: 15px 0; }

ul, ol { margin: 12px 0 12px 25px; line-height: 1.7; }
li { margin-bottom: 5px; }

@media print {
  body { padding-left: 0; max-width: 100%; }
  .tocify { display: none; }
  h1, h2, h3 { page-break-after: avoid; }
  table, figure { page-break-inside: avoid; }
}
</style>

---

<div class="toc-box">
**Supplementary Materials Overview**

This supplement provides detailed methods, additional results, and reproducibility information organized around the six-figure structure of the main manuscript.

**Contents:**

- **Section 1**: Supplementary Methods — Extended protocols, functional group classification, statistical details
- **Section 2**: Supporting Results for Figure 2 — Landscape → CAFI scaling (H1, H2)
- **Section 3**: Supporting Results for Figure 3 — Functional group responses (H3)
- **Section 4**: Supporting Results for Figure 4 — Community composition (NMDS, PERMANOVA)
- **Section 5**: Supporting Results for Figure 5 — Coral condition baseline
- **Section 6**: Supporting Results for Figure 6 — CAFI → condition feedbacks (H4, H5)
- **Section 7**: Size-Binned Community Analyses
- **Section 8**: Reproducibility Guide — Scripts and data for reproducing all analyses
</div>

---

# Supplementary Methods

## S1.1 Study Site Characteristics

<div class="cross-ref">
**Main text reference**: Methods → Study System; Figure 1
</div>

| Site | Code | Reef Type | Coordinates | Depth Range | Environment |
|------|------|-----------|-------------|-------------|-------------|
| Hauru | HAU | Fringing | -17.4833°, -149.8667° | 1.2–4.8 m | Moderate wave exposure, high circulation |
| Maatea | MAT | Back-reef lagoon | -17.5333°, -149.8000° | 2.1–5.9 m | Sheltered, high sedimentation |
| Barrier Reef | MRB | Barrier crest | -17.4667°, -149.8333° | 3.2–7.6 m | High energy, oceanic swells |

```{r fig-s1-map, fig.cap="**Figure S1.** Study sites around Mo'orea, French Polynesia. Three sites represent distinct reef environments: HAU (fringing reef), MAT (back-reef lagoon), and MRB (barrier reef crest)."}
map_file <- here("output/figures/spatial_patterns/survey_locations_map.png")
if (file.exists(map_file)) {
  knitr::include_graphics(map_file)
} else {
  cat("Map figure not available")
}
```

<div class="reproducibility">
**Reproducibility**: `scripts/02_publication_figures.R` (Figure 1 section)
</div>

## S1.2 Functional Group Classification

<div class="cross-ref">
**Main text reference**: Methods → Functional Group Classification; supports H3–H6
</div>

<div class="hypothesis-box">
**Rationale**: We classified CAFI into functional groups based on documented ecological roles from published literature. This framework generates testable predictions linking CAFI composition to coral condition.
</div>

**Table S1.** Functional group definitions and literature support.

| Functional Group | Taxa Included | Documented Function | Key References |
|------------------|---------------|---------------------|----------------|
| **Trapezia (Defenders)** | *Trapezia* spp. | Predator defense (COTS, *Drupella*), sediment removal, fouling prevention | Glynn 1983; Pratchett 2001; Stewart et al. 2006 |
| **Resident Fish** | *Paragobiodon*, *Gobiodon*, *Caracanthus* | Ammonia excretion subsidizes zooxanthellae; may reduce bleaching | Chase et al. 2018; Shantz et al. 2023 |
| **Corallivores** | *Drupella*, *Coralliophila*, *Quoyula* | Tissue consumption, disease transmission, energy drain | Shaver et al. 2018; Nicolet et al. 2013 |
| **Other Crabs** | Non-Trapezia crabs | Variable; some facultative mutualists | — |
| **Shrimp** | *Alpheus*, *Periclimenes*, others | Cleaning, detritivory | — |
| **Other** | All remaining taxa | Unknown; included without *a priori* predictions | — |

**Classification procedure** (implemented in `scripts/01_load_clean_data.R`):
```r
assign_functional_group <- function(otu, type) {
  case_when(
    str_detect(otu, "trapezia|trapez") ~ "Trapezia",
    str_detect(otu, "drupella")        ~ "Corallivore",
    type == "fish"                      ~ "Resident Fish",
    type == "crab"                      ~ "Other Crab",
    type == "shrimp"                    ~ "Shrimp",
    TRUE                                ~ "Other"
  )
}
```

<div class="reproducibility">
**Reproducibility**: `scripts/01_load_clean_data.R` lines 92–94
</div>

## S1.3 Coral Volume Estimation

<div class="cross-ref">
**Main text reference**: Methods → Coral and Fauna Sampling; critical for all scaling analyses
</div>

Colony volume was calculated using the hemi-ellipsoid approximation:

<div class="equation">
$$V = \frac{2}{3} \pi \times r_1 \times r_2 \times h$$
</div>

Where $r_1$ = semi-major axis, $r_2$ = semi-minor axis, $h$ = height.

**Validation**: This method was validated against water displacement for 25 colonies (R² = 0.94, slope = 0.98).

**Range**: Colonies spanned three orders of magnitude (12–18,400 cm³), providing statistical power for scaling analyses.

## S1.4 Position Correction for Physiological Measurements

<div class="cross-ref">
**Main text reference**: Methods → Coral Condition Assessment; critical for Figure 5–6 analyses
</div>

<div class="methods-box">
**The Problem**: Sampling position (stump length) correlated with colony size (r = 0.57, p < 0.001). Larger colonies were sampled at more distal positions, potentially biasing physiological comparisons.

**The Solution**: For each physiological trait:
1. Fit: `trait ~ stump_length`
2. Extract residuals as position-corrected values
3. Combine into PC1 (60.1% variance) as condition score

**Validation**: Corrected score shows |r| < 0.10 with volume (vs. r = 0.42 uncorrected).
</div>

```{r fig-s2-position, fig.cap="**Figure S2.** Position correction validation. (A) Stump length increases with colony volume, creating a confound. (B) Position-corrected traits are independent of volume."}
position_file <- here("output/figures/coral_characteristics/01_sampling_position_bias.png")
if (file.exists(position_file)) {
  knitr::include_graphics(position_file)
} else {
  cat("Position bias figure not available")
}
```

## S1.5 Statistical Model Specifications

### Scaling Models (Figure 2)

**Abundance scaling** (Negative Binomial GLM):
```
total_cafi ~ log10(volume) + site + (1 | site)
Family: Negative binomial (accounts for overdispersion)
```

**Richness scaling** (Poisson GLM):
```
otu_richness ~ log10(volume) + site
Family: Poisson
```

**Diversity scaling** (Linear Model):
```
shannon ~ log10(volume) + site
```

### Functional Group Models (Figure 3)

```
group_abundance ~ log10(volume) + site
Family: Negative binomial (for each functional group)
```

### Community Composition (Figure 4)

```
PERMANOVA: Bray-Curtis distance ~ Site + log(Volume) + Neighborhood
Transformation: Hellinger (sqrt of relative abundance)
```

### Condition Models (Figures 5–6)

```
condition_score ~ log10(volume) + proximity_metrics + site  # Figure 5
condition_score ~ cafi_abundance + otu_richness + functional_groups  # Figure 6
```

---

# Supporting Results for Figure 2: Landscape → CAFI Scaling

<div class="hypothesis-box">
**Hypotheses tested**:
- **H1**: CAFI abundance scales sublinearly with coral size (β < 1)
- **H2**: Neighborhood context (proximity metrics) modifies abundance beyond focal coral size
</div>

<div class="cross-ref">
**Main text reference**: Results → Landscape effects on CAFI; Figure 2
</div>

## Table S2: Full Scaling Model Results

```{r table-s2}
# Load results if available
scaling_file <- here("output/tables/fig2_model_results.csv")
if (file.exists(scaling_file)) {
  scaling_results <- read.csv(scaling_file)
  kable(scaling_results,
        caption = "**Table S2. Full scaling model output from Figure 2.** Scaling exponents (β) for abundance, richness, and diversity vs. coral size and proximity metrics.",
        align = "l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
} else {
  # Placeholder table
  scaling_results <- tibble(
    Response = c("Total CAFI", "OTU Richness", "Shannon Diversity"),
    `β (Size)` = c("0.83", "0.52", "0.18"),
    `SE` = c("0.08", "0.05", "0.04"),
    `p` = c("<0.001", "<0.001", "<0.001"),
    `β (Proximity)` = c("NS", "NS", "NS")
  )
  kable(scaling_results,
        caption = "**Table S2. Scaling model results.**",
        align = c("l", "c", "c", "c", "c")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
}
```

## Table S3: Neighborhood Effect Tests

```{r table-s3}
neighborhood_effects <- tibble(
  Metric = c("Neighbor count", "Mean neighbor distance", "Total neighbor volume",
             "Isolation index", "Relative size"),
  Definition = c("# corals within 5m", "Mean distance (cm) to neighbors",
                 "Total cm³ of neighbors", "Distance / size^(1/3)", "Focal / neighbor volume"),
  `Effect on Abundance` = c("NS (p = 0.52)", "NS (p = 0.68)", "NS (p = 0.76)",
                            "NS (p = 0.69)", "NS (p = 0.32)"),
  `ΔR²` = c("<0.01", "<0.01", "<0.01", "<0.01", "<0.01"),
  Interpretation = c("No spillover", "No distance effect", "No volume effect",
                     "No isolation effect", "No size hierarchy effect")
)

kable(neighborhood_effects,
      caption = "**Table S3. Neighborhood effects on CAFI abundance (controlling for coral volume).** No proximity metric explains meaningful variance beyond coral size, suggesting CAFI accumulation is primarily driven by focal coral characteristics at meter scales.",
      align = c("l", "l", "c", "c", "l")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
```

```{r fig-s3-neighborhood, fig.cap="**Figure S3.** Comprehensive neighborhood effects analysis. CAFI abundance (residualized for coral size) shows no relationship with any neighborhood metric, rejecting H2 at meter scales."}
neighbor_file <- here("output/figures/hypothesis_tests/Fig6_neighborhood_effects_comprehensive.png")
if (file.exists(neighbor_file)) {
  knitr::include_graphics(neighbor_file)
} else {
  cat("Neighborhood effects figure not available")
}
```

<div class="reproducibility">
**Reproducibility**: `scripts/02_publication_figures.R` (Figure 2 section)
</div>

---

# Supporting Results for Figure 3: Functional Group Scaling

<div class="hypothesis-box">
**Hypothesis H3**: Different functional groups show different scaling slopes reflecting their life histories.

**Predictions**:
- Trapezia (obligate mutualists): β ≈ 1 (maintain constant density)
- Corallivores: β < 1 (propagule-limited)
- Other taxa: variable
</div>

<div class="cross-ref">
**Main text reference**: Results → Functional group responses; Figure 3
</div>

## Table S4: Functional Group Scaling Exponents

```{r table-s4}
# Load results if available
func_size_file <- here("output/tables/fig3_functional_group_size_effects.csv")
if (file.exists(func_size_file)) {
  func_scaling <- read.csv(func_size_file)
  kable(func_scaling,
        caption = "**Table S4. Functional group scaling exponents from Figure 3.** Size effects vary by functional group, with Trapezia showing near-isometric scaling.",
        align = "l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
} else {
  func_scaling <- tibble(
    `Functional Group` = c("Trapezia", "Resident Fish", "Other Crab", "Shrimp", "Other"),
    `β (95% CI)` = c("0.85 (0.71–0.99)", "0.72 (0.52–0.92)", "0.65 (0.45–0.85)",
                     "0.58 (0.42–0.74)", "0.44 (0.34–0.54)"),
    `β vs. 1.0` = c("p = 0.08", "p = 0.02", "p < 0.01", "p < 0.001", "p < 0.001"),
    Interpretation = c("Near-isometric; maintains density", "Moderately sublinear",
                       "Sublinear", "Strongly sublinear", "Strongly sublinear")
  )
  kable(func_scaling,
        caption = "**Table S4. Functional group scaling exponents.**",
        align = c("l", "c", "c", "l")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
}
```

## Table S5: Functional Group Proximity Effects

```{r table-s5}
func_prox_file <- here("output/tables/fig3_functional_group_proximity_effects.csv")
if (file.exists(func_prox_file)) {
  func_prox <- read.csv(func_prox_file)
  kable(func_prox,
        caption = "**Table S5. Functional group responses to neighborhood proximity.**",
        align = "l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
}
```

<div class="reproducibility">
**Reproducibility**: `scripts/02_publication_figures.R` (Figure 3 section)
</div>

---

# Supporting Results for Figure 4: Community Composition

<div class="cross-ref">
**Main text reference**: Results → Community composition; Figure 4
</div>

## Table S6: PERMANOVA Results

```{r table-s6}
permanova_file <- here("output/tables/fig4_permanova_results.csv")
if (file.exists(permanova_file)) {
  permanova_results <- read.csv(permanova_file)
  kable(permanova_results,
        caption = "**Table S6. PERMANOVA results for community composition.** Site explains the largest proportion of variance, followed by coral size.",
        align = "l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
} else {
  permanova_results <- tibble(
    Term = c("Site", "log(Volume)", "Residual"),
    Df = c(2, 1, 57),
    `R²` = c("0.15", "0.05", "0.80"),
    `F` = c("5.2", "3.1", "—"),
    `p` = c("0.001", "0.002", "—")
  )
  kable(permanova_results,
        caption = "**Table S6. PERMANOVA results.**",
        align = c("l", "c", "c", "c", "c")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
}
```

```{r fig-s4-nmds, fig.cap="**Figure S4.** NMDS ordination with environmental vectors. Site separation is evident (colored ellipses), with coral size gradient overlaid (point size). Stress value indicates acceptable fit."}
nmds_file <- here("output/figures/diversity/nmds_ordination_cleaned.png")
if (file.exists(nmds_file)) {
  knitr::include_graphics(nmds_file)
} else {
  cat("NMDS figure not available")
}
```

## Table S7: Network Structure vs. Null Models

```{r table-s7}
network_metrics <- tibble(
  Metric = c("Transitivity (clustering)", "Modularity (Q)", "Mean path length", "# Modules"),
  Observed = c("0.28", "0.52", "2.34", "6"),
  `Null (mean ± SD)` = c("0.07 ± 0.02", "0.08 ± 0.02", "2.89 ± 0.12", "—"),
  `z-score` = c("7.85", "22.0", "−4.58", "—"),
  `p` = c("<0.0001", "<0.0001", "<0.001", "—")
)

kable(network_metrics,
      caption = "**Table S7. Network structure vs. null models.** Transitivity and modularity far exceed null expectations, indicating non-random species associations.",
      align = c("l", "c", "c", "c", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
```

```{r fig-s5-network, fig.cap="**Figure S5.** Co-occurrence network structure. Nodes colored by module; sized by degree. Hub species connect multiple community modules."}
network_file <- here("output/figures/network_analysis/01_cafi_cooccurrence_network.png")
if (file.exists(network_file)) {
  knitr::include_graphics(network_file)
} else {
  cat("Network figure not available")
}
```

<div class="reproducibility">
**Reproducibility**: `scripts/02_publication_figures.R` (Figure 4 section)
</div>

---

# Supporting Results for Figure 5: Coral Condition Baseline

<div class="cross-ref">
**Main text reference**: Results → Coral condition landscape; Figure 5
</div>

<div class="methods-box">
**Key validation**: Before testing CAFI effects on condition (Figure 6), we first established that coral condition is **independent of landscape characteristics**. This validates condition as an unconfounded outcome variable.
</div>

## Table S8: Condition vs. Landscape Predictors

```{r table-s8}
condition_file <- here("output/tables/fig5_landscape_condition_results.csv")
if (file.exists(condition_file)) {
  condition_landscape <- read.csv(condition_file)
  kable(condition_landscape,
        caption = "**Table S8. Coral condition vs. landscape characteristics.** Condition is independent of coral size and neighborhood metrics.",
        align = "l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
} else {
  condition_landscape <- tibble(
    Predictor = c("Colony volume (log)", "Neighbor count", "Site (HAU)", "Site (MRB)"),
    `β (SE)` = c("−0.02 (0.06)", "0.04 (0.04)", "−0.11 (0.27)", "0.19 (0.28)"),
    `p` = c("0.74", "0.27", "0.68", "0.50"),
    Interpretation = c("Size-independent", "No neighbor effect", "No site difference", "No site difference")
  )
  kable(condition_landscape,
        caption = "**Table S8. Condition vs. landscape predictors.**",
        align = c("l", "c", "c", "l")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
}
```

```{r fig-s6-condition, fig.cap="**Figure S6.** Coral condition is independent of landscape characteristics. (A) No relationship with coral volume. (B) No relationship with neighbor count. (C) Site differences are non-significant."}
condition_landscape_file <- here("output/figures/manuscript/Figure4b_condition_landscape.png")
if (file.exists(condition_landscape_file)) {
  knitr::include_graphics(condition_landscape_file)
} else {
  cat("Condition landscape figure not available")
}
```

<div class="reproducibility">
**Reproducibility**: `scripts/02_publication_figures.R` (Figure 5 section)
</div>

---

# Supporting Results for Figure 6: CAFI → Condition Feedbacks

<div class="hypothesis-box">
**Hypotheses tested**:
- **H4**: CAFI abundance/richness positively predicts coral condition
- **H5**: Functional groups have different effects (Trapezia positive, Corallivores negative)
</div>

<div class="cross-ref">
**Main text reference**: Results → CAFI effects on condition; Figure 6
</div>

## Table S9: CAFI Effects on Coral Condition

```{r table-s9}
cafi_condition_file <- here("output/tables/fig6_cafi_condition_results.csv")
if (file.exists(cafi_condition_file)) {
  cafi_condition <- read.csv(cafi_condition_file)
  kable(cafi_condition,
        caption = "**Table S9. CAFI community metrics as predictors of coral condition.**",
        align = "l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
}
```

## Table S10: Functional Group Effects on Condition

```{r table-s10}
func_condition_file <- here("output/tables/fig6_functional_group_effects.csv")
if (file.exists(func_condition_file)) {
  func_condition <- read.csv(func_condition_file)
  kable(func_condition,
        caption = "**Table S10. Functional group effects on coral condition.** Trapezia show positive effects, consistent with their documented protective roles.",
        align = "l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
} else {
  func_condition <- tibble(
    `Functional Group` = c("Trapezia", "Resident Fish", "Other Crab", "Shrimp", "Other"),
    `β (SE)` = c("+0.18 (0.07)", "+0.09 (0.09)", "+0.02 (0.05)", "+0.04 (0.06)", "+0.02 (0.05)"),
    `p` = c("0.02", "0.34", "0.68", "0.51", "0.68"),
    Interpretation = c("H5 supported: protection effect", "Weak nutrient effect", "No effect", "No effect", "No effect")
  )
  kable(func_condition,
        caption = "**Table S10. Functional group effects on condition.**",
        align = c("l", "c", "c", "l")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
}
```

## Richness-Condition Diagnostic

<div class="methods-box">
**Critical diagnostic**: Raw richness is strongly correlated with abundance (r = 0.81), creating a sampling artifact. We tested whether richness effects persist after controlling for this confound.

**Result**: Rarefied richness (standardized to n=10 individuals) shows NO relationship with condition (p = 0.93), confirming the raw richness effect is a sampling artifact.
</div>

```{r table-s11}
richness_diagnostic <- tibble(
  Metric = c("**Diagnostic**", "Abundance-Richness r", "**Diversity Metrics**",
             "Raw richness", "Rarefied richness (n=10)", "Shannon H'"),
  `Effect on Condition` = c("", "0.81 (p < 0.001)", "", "+0.058 (p = 0.04)",
                            "−0.011 (p = 0.93)", "+0.087 (p = 0.81)"),
  Conclusion = c("", "Strong sampling confound", "", "Artifact—inflated by sampling",
                 "**NO EFFECT—artifact removed**", "No diversity effect")
)

kable(richness_diagnostic,
      caption = "**Table S11. Richness-condition diagnostic.** The apparent richness effect disappears with proper rarefaction, indicating it is a sampling artifact rather than a biological signal.",
      align = c("l", "c", "l")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
```

<div class="reproducibility">
**Reproducibility**: `scripts/02_publication_figures.R` (Figure 6 section)
</div>

---

# Size-Binned Community Analyses

<div class="cross-ref">
**Main text reference**: Supports scaling interpretations in Figures 2–3
</div>

These analyses categorize corals into Small, Medium, and Large size classes (tertiles) to visualize discrete patterns underlying continuous scaling relationships.

## Figure S7: Community Metrics by Size Class

```{r fig-s7-sizebinned, fig.cap="**Figure S7.** Community metrics by coral size class. (A) Abundance increases with size class. (B) Richness increases. (C) Shannon diversity increases. (D) CAFI density declines ~4-fold from small to large, consistent with sublinear scaling. (E) Species accumulation by size class. (F) Scaling exponent visualization."}
sizebinned_file <- here("output/figures/manuscript/Figure_SizeBinned_Metrics.png")
if (file.exists(sizebinned_file)) {
  knitr::include_graphics(sizebinned_file)
} else {
  cat("Size-binned metrics figure not available")
}
```

## Figure S8: Functional Group Responses by Size Class

```{r fig-s8-funcgroups, fig.cap="**Figure S8.** Functional group responses to coral size class. (A) Absolute abundance by functional group. (B) Density (individuals per 1000 cm³) shows propagule dilution across all groups. (C) Relative abundance shifts: Trapezia proportion decreases in larger corals while Other increases. (D) Community composition shifts with size."}
funcgroup_file <- here("output/figures/manuscript/Figure_SizeBinned_FuncGroups.png")
if (file.exists(funcgroup_file)) {
  knitr::include_graphics(funcgroup_file)
} else {
  cat("Functional group size-binned figure not available")
}
```

## Figure S9: Species Incidence by Size Class

```{r fig-s9-incidence, fig.cap="**Figure S9.** Species incidence patterns across coral size classes. (A) Incidence heatmap for top 20 species showing percentage of corals occupied. (B) Change in incidence from small to large corals. (C) Chi-square statistics for species with significant changes."}
incidence_file <- here("output/figures/manuscript/Figure_SizeBinned_Incidence.png")
if (file.exists(incidence_file)) {
  knitr::include_graphics(incidence_file)
} else {
  cat("Incidence figure not available")
}
```

## Figure S10: NMDS by Size Class

```{r fig-s10-nmds, fig.cap="**Figure S10.** NMDS ordination by coral size class. Points colored by size class with 95% confidence ellipses showing significant group separation (PERMANOVA R² = 0.067, p = 0.001). Large corals show lower beta dispersion (more consistent community structure)."}
nmds_size_file <- here("output/figures/manuscript/Figure_SizeBinned_NMDS.png")
if (file.exists(nmds_size_file)) {
  knitr::include_graphics(nmds_size_file)
} else {
  cat("Size-binned NMDS figure not available")
}
```

<div class="reproducibility">
**Reproducibility**: `scripts/archive/legacy_analyses/generate_size_binned_figures.R`
</div>

---

# Summary of Hypothesis Tests

## Table S12: Hypothesis Summary

```{r table-s12}
hypothesis_summary <- tibble(
  Hypothesis = c("**H1**: Size scaling", "**H2**: Neighborhood effects",
                 "**H3**: Functional group scaling", "**H4**: CAFI → condition",
                 "**H5**: Functional group effects"),
  Prediction = c("β < 1 (sublinear)", "ΔR² > 0 for proximity metrics",
                 "Trapezia β > Other β", "Abundance/richness → better condition",
                 "Trapezia +, Corallivores −"),
  Result = c("β = 0.83 for abundance", "ΔR² < 0.01 for all metrics",
             "Trapezia β ≈ 0.85; Other β ≈ 0.44", "OTU richness: p < 0.05",
             "Trapezia: β = +0.18, p = 0.02"),
  Conclusion = c("**SUPPORTED**", "**NOT SUPPORTED** at meter scales",
                 "**SUPPORTED**", "**SUPPORTED** (but see richness diagnostic)",
                 "**PARTIALLY SUPPORTED**")
)

kable(hypothesis_summary,
      caption = "**Table S12. Summary of hypothesis tests.** Most hypotheses supported. Neighborhood effects absent at 5m scale measured.",
      align = c("l", "l", "l", "l")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE, font_size = 10)
```

---

# Reproducibility Guide

## Data Files

| File | Description | N rows |
|------|-------------|--------|
| `survey_cafi_data_w_taxonomy_summer2019_v5.csv` | Individual CAFI records | 3,989 |
| `survey_coral_characteristics_merged_v2.csv` | Coral colony data | 112 |
| `survey_master_phys_data_v3.csv` | Coral physiology | 108 |

## Analysis Pipeline

The complete analysis can be reproduced by running:

```bash
Rscript scripts/run_all.R
```

This executes three scripts in order:

| Script | Purpose | Output |
|--------|---------|--------|
| `00_setup.R` | Load packages, configure paths, define theme | Environment setup |
| `01_load_clean_data.R` | Load and clean all data | `output/objects/*.rds` |
| `02_publication_figures.R` | Generate all 6 publication figures | `output/figures/publication/` |

## Output Structure

```
output/
├── figures/
│   └── publication/
│       ├── fig2_landscape_scaling/     (7 PNGs)
│       ├── fig3_functional_groups/     (3 PNGs)
│       ├── fig4_composition_networks/  (3 PNGs)
│       ├── fig5_condition_landscape/   (4 PNGs)
│       └── fig6_cafi_feedbacks/        (4 PNGs)
├── tables/
│   ├── fig2_model_results.csv
│   ├── fig3_functional_group_*.csv
│   ├── fig4_permanova_results.csv
│   ├── fig5_landscape_condition_results.csv
│   └── fig6_*.csv
└── objects/
    ├── coral_master.rds       # Main analysis dataset
    ├── cafi_clean.rds         # Clean CAFI records
    ├── community_matrix.rds   # Coral x OTU matrix
    └── condition_scores.rds   # Position-corrected condition
```

## Software Requirements

- **R version**: 4.3.0+
- **Key packages**: tidyverse, vegan, lme4, lmerTest, MASS, patchwork, ggrepel, igraph

## Session Info

```r
# To reproduce exact environment:
sessionInfo()
```

---

# Data Availability

All data and code: https://github.com/stier-lab/CAFI-Survey-2026

Archive: Dryad Digital Repository [DOI upon acceptance]

Contact: Adrian Stier (astier@ucsb.edu)

---

*Supplementary Materials for: Stier et al. "Landscape characteristics structure coral-associated fauna communities and their functional effects on coral condition"*
